---
title: "assignment7"
author: "Subhasree Samanta"
date: "November 6, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
library(broom)
library(rvest)
library(readxl)

```

    
    
```{r}
xmart <- read.csv("xmart.csv")

##Removing extra spaces
xmart[,3] <-gsub(" ","", xmart[,3]) 

##Extracting bounds
xmart$lower_bound <- str_split_fixed(str_extract(xmart[,3],"\\[[ 0-9 -]+\\]"), "-", 2)[,1]
xmart$upper_bound <- str_split_fixed(str_extract(xmart[,3],"\\[[ 0-9 -]+\\]"), "-", 2)[,2]

##Removing brackets
xmart$lower_bound <- as.integer(gsub("\\[", "", xmart$lower_bound))
xmart$upper_bound <- as.integer(gsub("\\]","", xmart$upper_bound))

##Removing bounds from col3
xmart[,3] <- as.integer(gsub("\\[[ 0-9 -]+\\]", "", xmart[,3]))

##Change col names?

```

```{r}
gni <- read.csv("WHS9_93.csv", skip=1, as.is = TRUE, check.names = FALSE)

##Removing extra spaces from & changing class of 2013 to integer
gni[,2] <-as.integer(gsub(" ","", gni[,2]))

##Tidying data: Using gather to have one entry per country per year
gni <- gni %>%
  gather(year, value, 2:25)
```
- Download the gross national income data from http://apps.who.int/gho/data/node.main.GNI107?lang=en (Download the complete data as a "CVS table", storing it in the data folder).
- Tidy this data, so that there is one entry per country per year
- Merge the two files by country and year, retaining only rows for which you have per capita income and either maternal mortality or percentage attended births
- Make a two polished  and informative graphs, one relating income to maternal mortality and the other relating income to percentage attended births
- Save a csv file with the merged, cleaned, and tidy data, using a suitable name of your choosing in the data folder.
- Use the country_choropleth() function in the choroplethr package to make a world map of maternal mortality, using the most recent year for each country in the merged dataset you created. The defaults of the function will be fine; no need to tune up the plot. You can read the help file to see how the data must be formatted; you may need to rename the countries from the dataset that you've created.
- All of your steps, other than downloading the files, should be contained in a single R Markdown file that will run in the repo directory. Be sure to describe your steps
